CSE 517: Project Proposal

### 2019-03-17 cse517/report/main.tex
Starting report.

%
% File emnlp2018.tex
%
%% Based on the style files for EMNLP 2018, which were
%% Based on the style files for ACL 2018, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{emnlp2018}
\usepackage{times}
\usepackage{latexsym}

\usepackage{url}

% user packages
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage{booktabs}

%\aclfinalcopy % Uncomment this line for the final submission

@@

\newcommand\BibTeX{B{\sc ib}\TeX}
\newcommand\confname{EMNLP 2018}
\newcommand\conforg{SIGDAT}

\title{Title}

\author{
  Deric Pang$^\heartsuit$ \quad
  Author 2 \quad
  Author 3 \quad
  Author 4 \\
  $^\heartsuit$Paul G. Allen of Computer Science \& Engineering,
    University of Washington,
    Seattle, WA, USA \\
  $^\diamondsuit$Allen Institute for Artificial Intelligence, Seattle, WA,
    USA \\
  {\tt \{dericp, author2, author3, author4\}@cs.washington.edu} \\
}

@@

\begin{document}
\maketitle
\begin{abstract}
  We show that syntactic information is important when performing natural
  language inference (NLI). We describe new modeling techniques for NLI that
  improve upon previous baselines by adding minimal amounts of syntactic
  information.
\end{abstract}

@@

Natural language inference (NLI) is the task of characterizing entailment and
contradiction relationships between texts.
In general, most NLI tasks are formulated as characterizing the relationship
between a pair of sequences---a premise and a hypothesis. An NLI model should
predict whether the hyothesis is entailed by the premise, contradicts the
premise, or is neutral to the premise.

We seek to improve models which
perform NLI by adding syntactic features into existing models. In particular,
we investigate the well-known decomposable attention (DA) neural network
\citep{Parikh2016-em} which obtained state of the art results on the
SNLI \citep{Bowman2015-is} dataset at its time of publication while using
drastically fewer parameters than previous NLI models.

We extend the DA model and evaluate new models on SNLI, MultiNLI
\citep{Williams2017-uh}, the SNLI and MultiNLI hard splits
\citep{Gururangan2018-lj}, and smaller, domain specific datasets like Scitail
\citep{Khot2018-th}.

@@

\section{Credits}

\bibliography{references}
\bibliographystyle{acl_natbib_nourl}

>>>>

%
% File acl2018.tex
%
%% Based on the style files for ACL-2017, with some changes, which were, in turn,
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2019}
\usepackage{times}
\usepackage{latexsym}
\usepackage{url}
\usepackage{graphicx}
\usepackage{booktabs}

\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{CSE 517: Project Proposal}

\author{
  Deric Pang \quad
  Joshua Bean \\
  Paul G. Allen School of Computer Science \& Engineering \\
  University of Washington \\
  Seattle, WA, USA \\
  {\tt \{dericp, jbean96\}@cs.washington.edu} \\
}

@@

\begin{document}
\maketitle

@@

Natural language inference (NLI) is the task of characterizing entailment and
contradiction relationships between texts.  We seek to improve models which
perform NLI by adding syntactic features into existing models. In particular,
we will primarily investigate the well-known decomposable attention (DA) neural
network \citep{Parikh2016-em} which obtained state of the art results on the
SNLI \citep{Bowman2015-is} dataset at its time of publication while using
drastically fewer parameters than previous NLI models.

We intend to extend the DA model and evaluate new models on SNLI, MultiNLI
\citep{Williams2017-uh}, the SNLI and MultiNLI hard splits
\citep{Gururangan2018-lj}, and smaller, domain specific datasets like Scitail
\citep{Khot2018-th}.

In general, most NLI tasks are formulated as characterizing the relationship
between a pair of sequences---a premise and a hypothesis. An NLI model should
predict whether the hyothesis is entailed by the premise, contradicts the
premise, or is neutral to the premise.

@@

\bibliographystyle{acl_natbib}
\bibliography{main}
